Visualizations: Metropolitan Areas per Capita, Wave I, II, III (Deaths)

### 2020-12-05 KPMG Team/Dashboard/visualization_scripts/msa-waves-pax.Rmd
dashboard done
Dashboard Update
All tabs, viz of US Waves and Clusters

@@

# MSA Things
# from Sydney
msa_index <- read_csv("data/msa/msa_mix_index.csv") # csa and msa with population 
covid <- read_csv("data/msa/us_daily_msa_split_2020-11-16.csv") # split 
covid_state <- read_csv("data/us_state_level_clean_2020-11-20.csv") # states only

@@

covid_state
```

@@

View(state_reg_w2_start)
View(state_reg_total)
View(state_all)

>>>>

install.packages("profvis")
library(profvis)

@@

# MSA Things
# from Sydney
# msa_index <- read_csv("data/msa/msa_mix_index.csv") # csa and msa with population 
# covid <- read_csv("data/msa/us_daily_msa_split_2020-11-16.csv") # split 
# covid_state <- read_csv("data/us_state_level_clean_2020-11-20.csv") # states only

msa_index <- read_csv("data/msa/msa_mix_index.csv") # csa and msa with population
covid <- read_csv("data/msa/us_daily_msa_final_2020-12-02.csv") # split
covid_state <- read_csv("data/us_state_level_clean_2020-12-02.csv") # states only

@@

@@
